### 2019-08-30 Manuscript_postsubmission.Rmd
added post submission version of manuscript to include further improvements and corrections

  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig. \@ref(figure1)). These present a significant morphological variation across species [@mapstone2014global] (Fig. \@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization. A siphonophore is a colony bearing many feeding polyps (Fig. \@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules). Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla. While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey. When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy]. In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].

@@

In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv). When fitting all covariance terms simultaneously (Appendix 20.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities. This excluded many of the morphometric characters which are linearly dependent on other characters. Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states. To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes. These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset. Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 20). Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.

@@

The variance covariance matrices (Appendix 20.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig. \@ref(figure8)a. However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block. These results were not very sensitive to transformation of inapplicable states and taxon sampling. When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche. When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.6).

@@

We wish to thank the crew and scientists of the R/V Western Flyer, who participated in the collection of many of the specimens used in this study. We also want to thank Lynne Christianson and Shannon Johnson from the Monterey Bay Aquarium Research Institute for their assistance in the field as well as for sequencing some of the species included in this phylogeny. In addition, we wish to thank Lourdes Rojas, Daniel Drew, and Eric Lazo-Wasem for their assistance in imaging the fixed specimens and managing the collections. We thank Dennis Pilarczyk for organizing the prey selectivity data, and Joaquin Nunez for reviewing this manuscript. Furthermore, we thank Elizabeth D. Hetherington and C. Anela Choy for collating the data on siphonophore feeding and for reviewing the manuscript. Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us valuable knowledge about siphonophores.

>>>>

  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig. \@ref(figure1)). These present a significant morphological variation across species [@mapstone2014global] (Fig. \@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization. A siphonophore is a colony bearing many feeding polyps (Fig. \@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules). Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla. While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey. When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy]. In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent]. Siphonophores bear four major nematocyst types in their tentacles and tentilla. The largest type, heteronemes, have open-tip tubules characterized by bearing a distinctly wider spiny shaft at the proximal end of the everted tubule. These are typically found flanking the proximal end of the cnidoband. The most abundant type, haplonemes, have no distinct shaft, but similarly to heteronemes, their tubules have open tips and can be found in the cnidoband. Both heteronemes and haplonemes bear short spines along the tubule and can be toxic and penetrate the surface of some prey types. In the terminal filament, siphonophores bear two other types of nematocysts, characterized by their adhesive function, closed tip tubules, and lack of spines on the tubule. These are the desmonemes (a type of adhesive coiled-tubule spironeme), and rhopalonemes (a siphonophore-exclusive nematocyst type with wide tubules).

@@

In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv). When fitting all covariance terms simultaneously (Appendix 19.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities. This excluded many of the morphometric characters which are linearly dependent on other characters. Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states. To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes. These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset. Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 19). Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.

@@

The variance covariance matrices (Appendix 19.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig. \@ref(figure8)a. However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block. These results were not very sensitive to transformation of inapplicable states and taxon sampling. When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 19.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche. When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 19.6).

@@

We wish to thank the crew and scientists of the R/V Western Flyer, who participated in the collection of many of the specimens used in this study. We also want to thank Lynne Christianson and Shannon Johnson from the Monterey Bay Aquarium Research Institute for their assistance in the field as well as for sequencing some of the species included in this phylogeny. In addition, we wish to thank Lourdes Rojas, Daniel Drew, and Eric Lazo-Wasem for their assistance in imaging the fixed specimens and managing the collections. We thank Dennis Pilarczyk for organizing the prey selectivity data, Michael Landis for helping design the Bayesian analyses, and Joaquin Nunez for reviewing this manuscript. Furthermore, we thank Elizabeth D. Hetherington and C. Anela Choy for collating the data on siphonophore feeding and for reviewing the manuscript. Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us valuable knowledge about siphonophores.
